\input{title.tex}

### 2022-05-29 docs/papers/01_manuscript/01_introduction.tex
feat(appendix,-discussion): re-organized discussion, add sensitive analysis, re-organized method appendix
BREAKING CHANGE:

% 黄河的介绍
The Yellow River Basin (YRB), the fifth large river worldwide, is known for its irreplaceable role in the social-economic development of China, and thus also drastically interference by anthropogenic stress.
Supporting $35.63\%$ irrigation and $30\%$ population with only $2.66\%$ water resources of China (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: \today), the overburdened Yellow River dried up in consecutive years, resulting in substantial ecological, economic and social crisis (e.g., wetland shrink, agriculture reduction, and scramble for water).
Intense water use, accounting for about $80\%$ of Yellow River surface runoff in the 1980s, was remarked as the significant reason for the degradation.
Furthermore, human interferences such as soil conservation and water conservancy project boosted water withdrawal and then stressed the water scarcity of the Yellow River.
In the context of future climate change, the contradiction between supplies and demands of water resources in the YRB will become more prominent.
%! Citation: Hao Wang presentation.
Therefore, balancing ecological and developing demands in such a human-dominated basin is a problem for China in terms of water governance throughout and for large rivers worldwide.

% 第三段 过去管理的经验，断流的严重程度，连续多少没有断流，少有的解决断流的大河。治理成功的流域？分析背后的机制，基础。往用水上靠。
% 为了缓解用水压力
Chinese authorities implemented several ambitious water management practices in the YRB in the last century to relieve the water stress, such as reservoir regulation, South-to-north Water Diversion Project (WDP), and Water Allocation Scheme since 1987 (87-WAS), and the Unified Basinal Regulation since 1998 (98-UBR).
Through those efforts, ecological restoration of wetland and estuary delta in the YRB without drying up for over $20$ is widely considered a considerable river management achievement.
Different from the engineering of WDP provides further water supply or reservoir matches water supply and demands, institutional strategies like the 87-WAS (assign water quotas for provinces in the YRB) and the 98-UBR (the provinces had to be allowed to use water by the Yellow River Conservancy Commission, YRCC) mainly focused on limiting demands of water use.
Such institutions (policies, laws, and norms) can influence regional sustainability by changing the structure of the coupled human and natural system, including interplays between social actors, ecological units, or between social and ecological system elements \cite{young2008,cumming2020b,lien2020, bodin2017b}.
Understanding those complex interlinkages, therefore, is crucial for developing strategies to effectively manage natural resources and enhance the resilience of social-ecological systems (SES) \cite{kluger2020}.
However, while literature had well evaluated and quantified the effects of engineering solutions beforehand, there are few attempts to assess institutional contributions to successful water governance.

% 第四段 目标 制度变化。是不是制度变化产生的，如果是的话怎么影响。
In addition to widespread recognition of the rising importance of institutions as an approach to water sustainable use within large river basins (especially transboundary rivers like the YRB), their specific effects are still in open discussion \cite{agrawal2003, persha2011, agrawal2001}.
Effective (``matched'' or ``fit'') institutions operate at appropriate spatial, temporal, and functional scales to manage and balance different relationships and interactions between human and water systems, therefore, supporting (but do not guarantee) sustainability of SES \cite{epstein2015, wang2019d}.
Some institutional shifts have desirable water governance outcomes (e.g., the Ecological Water Diversion Project in Heihe River Basin, China \cite{wang2019d} and collaborative water governance systems in Europe \cite{green2013}).
However, shifting institutions in a large, complex river basin may create or destroy hundreds of different connections between social agents and ecological units, where matched social-ecological structures are not ubiquitous.
Therefore, the role of institutional shifts in the water governance achievement of the YRB and their impacts on water use is still uncertain without an understanding of SES structures.
% 通过抽象文件变化
Here, by abstracting changes in official documents following institutional shifts (the 87-WAS and the 98-UBR), we depicted the SES structures of the YRB from 1975 to 2008.
Then, we use Differenced Synthetic Control (DSC) method, which considers economic growth and natural background, to estimate theoretical water use scenarios without the institutional shifts (\textit{\hyperref[{sec:methods}]{Methods}} and \textit{Appendix~\nameref{secS2}}).
By further interpreting the differences of the effects in the YRB, we explored the mechanisms linking SESs structure and outcomes for a deeper understanding of institutions' role in water governance worldwide.

>>>>

% 黄河的介绍
The Yellow River Basin (YRB), the fifth large river worldwide, is known for its irreplaceable role in the social-economic development of China, and thus also drastically interference by anthropogenic stress.
Supporting $35.63\%$ irrigation and $30\%$ population with only $2.66\%$ water resources of China (data from \href{http://www.yrcc.gov.cn}{http://www.yrcc.gov.cn}, last access: \today), the overburdened Yellow River depleted in consecutive years, resulting in substantial ecological, economic and social crisis (e.g., wetland shrink, agriculture reduction, and scramble for water).
Intense water use, accounting for about $80\%$ of Yellow River surface runoff in the 1980s, was remarked as the significant reason for the degradation.
Furthermore, human interferences such as soil conservation and water conservancy project boosted water withdrawal and then stressed the water scarcity of the Yellow River.
In the context of future climate change, the contradiction between supplies and demands of water resources in the YRB will become more prominent.
%! Citation: Hao Wang presentation.
Therefore, balancing ecological and developing demands in such a human-dominated basin is a problem for China in terms of water governance throughout and for large rivers worldwide.

% 第三段 过去管理的经验，断流的严重程度，连续多少没有断流，少有的解决断流的大河。治理成功的流域？分析背后的机制，基础。往用水上靠。
% 为了缓解用水压力
Chinese authorities implemented several ambitious water management practices in the YRB in the last century to relieve the water stress, such as reservoir regulation, South-to-north Water Diversion Project (WDP), and Water Allocation Scheme since 1987 (87-WAS), and the Unified Basinal Regulation since 1998 (98-UBR).
Through those efforts, ecological restoration of wetlands and estuary delta in the YRB without drying up for over $20$ is widely considered a considerable river management achievement.
Different from the engineering that provides further water supply, institutional strategies like the 87-WAS (assign water quotas for provinces in the YRB) and the 98-UBR (the provinces had to be allowed to use water by the Yellow River Conservancy Commission, YRCC) mainly focused on limiting demands of water use.
Such institutions (policies, laws, and norms) can influence regional sustainability by changing the structure of the coupled human and natural system, including interplays between social actors, ecological units, or between social and ecological system elements \cite{young2008,cumming2020b,lien2020, bodin2017b}.
Understanding those complex interlinkages, therefore, is crucial for developing strategies to effectively manage natural resources and enhance the resilience of social-ecological systems (SES) \cite{kluger2020}.
However, while literature had well evaluated and quantified the effects of engineering solutions beforehand, there are few attempts to assess institutional contributions to successful water governance.

% 第四段 目标 制度变化。是不是制度变化产生的，如果是的话怎么影响。
In addition to widespread recognition of the rising importance of institutions as an approach to water sustainable use within large river basins (especially transboundary rivers like the YRB), their specific effects are still in open discussion \cite{agrawal2003, persha2011, agrawal2001}.
Effective (``matched'' or ``fit'') institutions operate at appropriate spatial, temporal, and functional scales to manage and balance different relationships and interactions between human and water systems, therefore, supporting (but not guaranteeing) the sustainability of SES \cite{epstein2015, wang2019d}.
Some institutional shifts have desirable water governance outcomes (e.g., the Ecological Water Diversion Project in Heihe River Basin, China \cite{wang2019d} and collaborative water governance systems in Europe \cite{green2013}).
However, shifting institutions in a large, complex river basin may create or destroy hundreds of different connections between social agents and ecological units, where matched social-ecological structures are not ubiquitous.
Therefore, the role of institutional shifts in the water governance achievement of the YRB and their impacts on water use is still uncertain without an understanding of SES structures.
% 通过抽象文件变化
Here, by abstracting changes in official documents following institutional shifts (the 87-WAS and the 98-UBR), we depicted the SES structures of the YRB from 1979 to 2008.
Then, we use Differenced Synthetic Control (DSC) method, which considers economic growth and natural background, to estimate theoretical water use scenarios without the institutional shifts (\textit{\hyperref[{sec:methods}]{Methods}} and \textit{Appendix~\nameref{secS2}}).
By further interpreting the differences of the effects in the YRB, we explored the mechanisms linking SESs structure and outcomes for a deeper understanding of institutions' role in water governance worldwide.

### 2022-05-29 docs/papers/01_manuscript/02_structures.tex
feat(appendix,-discussion): re-organized discussion, add sensitive analysis, re-organized method appendix
BREAKING CHANGE:

% 制度变动综述
% Including the national authorities, the basin management authorities, provinces, cities, and even districts, top-down institutional structures of the YRB started to evolve up to now (\textit{S1 in Supplementary Material}).
% As a pioneer in water governance shifting in China, the YRB started to explore a water allocating scheme since 1970s.
The institutional shifts in 1987 (87-WAS) and 1998 (98-UBR) were two widely recognized milestones in restricting water use among national water governance practices (\textit{Appendix}~\nameref{secS1}).
Until the 87-WAS, stakeholders (the provinces in the YRB) had free access to the YR water resources for development, but there were geographic and temporal differences between freshwater demand and availability.
As a compounded result of development, the provinces such as Shandong, Henan and Inner Mongolia used more water resources in the YRB with larger economies (primarily for irrigation agriculture).
For shrinking water deficits, national authorities proposed in 87-WAS allocating specific water quotas between $10$ provinces (or regions) along the YR basin.
However, the controversial scheme helped little in turning the water depletion around until another strategy attempted to strengthen the responsibilities of the YRCC in integrated water management in 1998 (the 98-UBR).
Therefore, our analysis period spans from 1979 (emergence of river depletion) to 2008 (a further polish of the 98-UBR), with the SESs shifted between three varying institutions (Figure~\ref{structure}).

We selected institutional regulatory documents on water use issued by national ministries (for validation to both watershed and regional agents) and extracted the interactions between the agents involved (\textit{Appendix \nameref{secS1}}).
Before 1987, the YRCC had no links to the provinces regarding water use, and the provinces could link to the Yellow River reaches directly (Figure~\ref{structure}).
However, according to the extracted information from the 87-WAS, the YRCC started to report water use from the provinces.
Furthermore, information from the 98-UBR documents demonstrated that the provinces had to apply their plan for an annual water use licence instead of direct access to the Yellow River water.
Thus, there have been links between the YRCC and the provinces since the strengthening responsibilities of the YRCC in 1998.

\begin{figure*}[!htb]
    \includegraphics[width=\linewidth]{diagrams/diagram.pdf}
	\caption{
		% 黄河流域的制度变迁与经济社会结构差异。
		Institutional shifts and related SES structures in the Yellow River Basin (YRB).
		\textbf{A.} The YBR crosses $10$ provinces or the same-level administrative regions, $8$ of which are highly relying on the water resources from the YRB (see \textit{Appendix \nameref{secS1}} Table~\ref{tab:quota}). The national administrations are the ultimate authority in issuing water governance policies, which are often implemented by basin-level agency (the Yellow River Conservancy Commission, YRCC) and each province-level agency.
		\textbf{B.} Since the YRCC does not use but monitor water, the provincial administrative agencies are the major stakeholders. Since the 87-WAS, with surface water withdraw from the Yellow River restricted by specific quotas, each stakeholder seperatly develop by planning and using fundamental water resources. However, the natural hydrological processes are connected. Although the institutions focus mainly on the surface water (Sur.), it can also influence groundwater inside (Gro.) or water resources outside (Sur. and Gro.'), through systematic socio-hydrological processes within the YRB.
		\textbf{C.} Institutional shifts and following structures changes (details in \textit{Appendix \nameref{secS1}}). (1) From 1979 to 1987, water resources were freely accessible to each stakeholder (denoted by red circles) from connected ecological unit (the reach of Yellow River, denoted by the blue circles). (2) After 1987-WAS, the YRCC (the yellow circles) was monitoring (the dot-line links) river reaches with the water use quota. (3) Since the 98-UBR, stakeholders have to apply water use licences from the YRCC (the connections between the red and yellow circles).
	}
	\label{structure}
\end{figure*}

>>>>

% 制度变动综述
The institutional shifts in 1987 (87-WAS) and 1998 (98-UBR) were two widely recognized milestones in restricting water use among national water governance practices (\textit{Appendix}~\nameref{secS1}).
Until the 87-WAS, stakeholders (the provinces in the YRB) had free access to the YR water resources for development, but there were geographic and temporal differences between freshwater demand and availability.
As a compounded result of development, the provinces such as Shandong, Henan, and Inner Mongolia used more water resources in the YRB with larger economies (primarily for irrigation agriculture).
For shrinking water deficits, national authorities proposed in 87-WAS allocating specific water quotas between $10$ provinces (or regions) along the YR basin (Table~\ref{tab:quota}).
However, the controversial scheme helped little in turning the water depletion around until another strategy attempted to strengthen the responsibilities of the YRCC in integrated water management in 1998 (the 98-UBR).
Therefore, our analysis period spans from 1979 (emergence of river depletion) to 2008 (a further polish of the 98-UBR), with the SESs shifted between three varying institutions (Figure~\ref{structure}).

We selected institutional regulatory documents on water use issued by national ministries (for validation to both watershed and regional agents) and then extracted the interactions between the agents involved (\textit{Appendix \nameref{secS1}}).
Before 1987, the YRCC had no links to the provinces regarding water use, and the provinces could link to the Yellow River reaches directly (Figure~\ref{structure}).
However, according to the extracted information from the 87-WAS, the YRCC started to report water use from the provinces.
Furthermore, information from the 98-UBR documents demonstrated that the provinces had to apply their plan for an annual water use license instead of direct access to the Yellow River water.
Thus, there have been links between the YRCC and the provinces since the strengthening responsibilities of the YRCC in 1998.

\begin{figure*}[!htb]
    \includegraphics[width=\linewidth]{diagrams/diagram.pdf}
	\caption{
		% 黄河流域的制度变迁与经济社会结构差异。
		Institutional shifts and related SES structures in the Yellow River Basin (YRB).
		\textbf{A.} The YBR crosses $10$ provinces or the same-level administrative regions, $8$ of which are highly relying on the water resources from the YRB (see \textit{Appendix \nameref{secS1}} Table~\ref{tab:quota}). The national administrations are the ultimate authority in issuing water governance policies, which are often implemented by basin-level agency (the Yellow River Conservancy Commission, YRCC) and each province-level agency.
		\textbf{B.} Provincial administrative agencies are the major stakeholders. Since the 87-WAS, with surface water withdrawal from the Yellow River restricted by specific quotas, each stakeholder plan and use water resources for development. However, the natural hydrological processes are connected. Although the institutions focus mainly on surface water (Sur.), it can also influence groundwater inside (Gro.) or water resources outside (Sur. and Gro.') through systematic socio-hydrological processes within the YRB. The YRCC only monitors water withdrawals at that time.
		\textbf{C.} Institutional shifts and following structures changes (details in \textit{Appendix \nameref{secS1}}). (1) From 1979 to 1987, water resources were freely accessible to each stakeholder (denoted by red circles) from the connected ecological unit (the reach of Yellow River, denoted by the blue circles). (2) After 1987-WAS, the YRCC (the yellow circles) was monitoring (the dot-line links) river reaches with the water use quota. (3) Since the 98-UBR, stakeholders have to apply for water use licenses from the YRCC (the connections between the red and yellow circles).
	}
	\label{structure}
\end{figure*}

### 2022-05-29 docs/papers/01_manuscript/03_results.tex
feat(appendix,-discussion): re-organized discussion, add sensitive analysis, re-organized method appendix
BREAKING CHANGE:

%\subsection{REGIONAL DIFFERENCES IN RESPONSES TO INSTITUTIONAL SHIFTS}
\subsection{Institutional effects on regulating differences}
\label{result-3}
% 结果2部分：展示区域相应差异
Our results also suggest differences between patterns of provinces in their responses to the two institutional regulating.
During the decade after the 87-WAS, the major water-using provinces (e.g., Inner Mongolia, Henan, Shandong) had apparent accelerations (Figure~\ref{regulating}).
The proportion of increased (or decreased) water use for each province (over the estimated water use by the model) has a significant correlation (partial correlation coefficient is $0.77$, $p<0.05$) to the actual water use from the Yellow River.
On everage, the major water users (Shandong, Inner Mongolia, Henan and Ningxia) used $32.14\%$ more water uses than the prediction from 1987 to 1998.
By contrast, after the 98-UBR (from 1998 to 2008), almost all provinces have seen evident ($-16.54\%$ on average) declines in water use.
The only exception is Inner Mongolia, whose water use throughout still exceeded the quota, but also considerably slowdown ($74.39\%$ decreased than the decade after 87-WAS) its rising.
Furthermore, the regulated water use of provinces was irrelevant (partial correlation coefficient is $0.33$, $p>0.1$) with their water use from the Yellow River in proportions.

\begin{figure*}[!tb]
    \centering
    \includegraphics[width=32pc]{outputs/fig3.pdf}
    \caption{
        Regulating differences for provinces in the YRB.
        Red and green bars denote actual water use over the estimation from the model in a decade after the institutional shift -the 87-WAS and the 98-UBR, respectively.
        The grey bars indicate the proportions of actual water use for each province to total water use of the provinces in a decade after the institutional shift.
        The triangles mark the water quotas assigned in the institution, scaled into ratios by the same total actual water use, too.
    }
    \label{regulating}
\end{figure*}

>>>>

%\subsection{REGIONAL DIFFERENCES IN RESPONSES TO INSTITUTIONAL SHIFTS}
\subsection{Heterogeneous institutional effects}
\label{result-3}
% 结果2部分：展示区域相应差异
Our results also suggest differences between patterns of provinces in their responses to the two institutional regulating.
During the decade after the 87-WAS, the major water-using provinces (e.g., Inner Mongolia, Henan, Shandong) had apparent accelerations (Figure~\ref{regulating}).
The proportion of increased (or decreased) water use for each province (over the estimated water use by the model) has a significant correlation (partial correlation coefficient is $0.77$, $p<0.05$) to the actual water use from the Yellow River.
On average, the major water users (Shandong, Inner Mongolia, Henan, and Ningxia) used $32.14\%$ more water use than the prediction from 1987 to 1998.
By contrast, after the 98-UBR (from 1998 to 2008), almost all provinces have seen evident ($-16.54\%$ on average) declines in water use.
Furthermore, the regulated water use of provinces was irrelevant (partial correlation coefficient is $0.33$, $p>0.1$) with their water use from the Yellow River in proportions.

\begin{figure*}[!tb]
    \centering
    \includegraphics[width=32pc]{outputs/fig3.pdf}
    \caption{
        Regulating differences for provinces in the YRB.
        Red (the 87-WAS) and green bars (the 98-UBR) denote an increased or decreased ratio for the actual water use over the estimation from the model in a decade after the institutional shift.
        The grey bars indicate the proportions of actual water use for each province to their total water use in a decade after the institutional shift.
        The triangles mark the water quotas assigned in the institution, scaled into ratios by dividing by their sum, too.
    }
    \label{regulating}
\end{figure*}
